Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-28 experiments.tex
added comment

Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
dispersion errors for different benchmarks for PS and GA
exploration. As it can be observed, GA still shows a tendency in
discovering more uniformly dispersed points (i.e. higher values in the
chart). These results,
together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
(b) confirm the the availability of density vs extension trade-offs
when comparing PS and GA approaches. Again, it
should be pointed out how a definitive claim about the superiority of
the PS behaviour is stricly dependent on the design 
requirements and constraints, e.g. whether we need wide or dense
results. Nevetheless, the proposed algorithm introduces a new
perspective on thinking the allocation of a simulations budget, paving the way for
the development of further strategies for addressing the problem of
multi-objective hardware/software desing space exploration.

>>>>

\comment{DP:il discorso si concludeva troppo di botto, ho aggiunto una
specie di finale che devi immaginare tipo il finale di rocky ''se io posso cambiare, e tu puoi
cambiare, tutto il mondo puo' cambiare, adriaaaanaa! ''}
Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
dispersion errors for different benchmarks for PS and GA
exploration. As it can be observed, GA still shows a tendency in
discovering more uniformly dispersed points (i.e. higher values in the
chart). These results,
together with the variation ranges of Fig.~\ref{fig:dispersion}(a) and
(b) confirm the the availability of density vs extension trade-offs
when comparing PS and GA approaches. Again, it
should be pointed out how a definitive claim about the superiority of
the PS behaviour is stricly dependent on the design 
requirements and constraints, e.g. whether we need wide or dense
results. Nevetheless, the proposed algorithm introduces a new
perspective on thinking the allocation of a simulations budget, paving the way for
the development of further strategies for addressing the problem of
multi-objective hardware/software desing space exploration.
